\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Alihan Baysal} & Email : \href{mailto:baysal.alihan@outlook.com}{baysal.alihan@outlook.com}\\
  \href{https://alihanbaysal.com}{alihanbaysal.com} $|$ \href{https://linkedin.com/in/alihanbaysal}{linkedin.com/in/alihanbaysal} $|$ \href{https://github.com/alihanbays}{github.com/alihanbays} & Mobile : +1-541-740-9292 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Corvallis, OR}
      {Bachelor of Science in Computer Science;  GPA: 3.98}{Sept. 2019 -- Mar. 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Blue Cross of Idaho (via In Time Tec)}{Los Angeles, CA}
      {Full Stack Engineer}{Oct. 2024 - Present}
      \resumeItemListStart
        \resumeItem{Backend API Development}
          {Developed RESTful APIs using .NET Core and Entity Framework Core for HIPAA-compliant healthcare applications, implemented OAuth2.0 authentication and role-based authorization, designed efficient database schemas with SQL Server optimizing complex queries and relationships.}
        \resumeItem{Full-Stack Application Development}
          {Built and maintained full-stack web applications on AWS (Lambda, RDS, S3), implemented business logic for patient data workflows, integrated third-party healthcare APIs, wrote comprehensive unit and integration tests using xUnit.}
        \resumeItem{FHIR Healthcare Integration}
          {Engineered HL7 FHIR-compliant data transformation services for interoperable healthcare data exchange, designed API contracts for external system integration, implemented data validation and error handling for robust healthcare data processing.}
        \resumeItem{Software Architecture \& Best Practices}
          {Designed scalable application architecture following SOLID principles and design patterns, participated in code reviews and technical design discussions, utilized CI/CD workflows for automated testing and deployment on AWS infrastructure.}
      \resumeItemListEnd

    \resumeSubheading
      {OSU Center for Applied Systems and Software}{Corvallis, OR}
      {Student Software Developer}{Feb. 2022 - July 2024}
      \resumeItemListStart
        \resumeItem{Microservices Architecture Migration}
          {Led migration from monolithic system to microservices architecture using .NET Core, designed event-driven communication patterns with ActiveMQ message broker, implemented API gateway for service orchestration and load balancing.}
        \resumeItem{Frontend Development}
          {Built responsive SPAs using Vue.js 3 with Composition API, implemented Vuex for centralized state management, integrated RESTful API consumption with Axios, ensuring type safety with TypeScript throughout component hierarchy.}
        \resumeItem{Backend \& Integration}
          {Developed RESTful APIs using .NET Core and Entity Framework, implemented asynchronous messaging patterns with ActiveMQ for decoupled service communication, wrote unit tests with xUnit and integration tests for API endpoints.}
        \resumeItem{Code Quality \& Collaboration}
          {Participated in code reviews using Git workflows, followed Agile development practices with sprint planning and retrospectives, documented technical specifications and API contracts for cross-team integration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Twitter Clone | \href{https://github.com/alihanbays/twitter-clone}{github.com/alihanbays/twitter-clone}}
      {Full-stack social media web app built with C\#, .NET 8, and ASP.NET Core. Implemented user authentication with session management, tweet CRUD operations with SQLite database, many-to-many relationships for follow system, and dynamic timeline rendering. Designed RESTful API architecture and wrote unit tests with xUnit achieving comprehensive test coverage.}
    \resumeSubItem{Daily LeetCode Scraper | \href{https://github.com/alihanbays/Daily-LeetCode-Scraper}{github.com/alihanbays/Daily-LeetCode-Scraper}}
      {C\# .NET console application that scrapes LeetCode's daily challenge using HTTP requests and HTML parsing, formats problem data, and publishes to Microsoft Teams via webhook integration. Deployed on Raspberry Pi with scheduled execution using cron for automated daily team collaboration.}
    \resumeSubItem{YouTube Clone | \href{https://github.com/alihanbays/youtube-clone}{github.com/alihanbays/youtube-clone}}
      {Full-stack video platform built with TypeScript, implementing video upload/streaming functionality, user authentication, and responsive UI demonstrating modern web development architecture and type-safe programming practices.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C\#, Python, TypeScript, JavaScript, SQL, C++}
   }
   \item{
     \textbf{Frameworks}{: .NET Core/.NET 8, ASP.NET Core, Entity Framework Core, Vue.js 3, Razor Pages, xUnit}
   }
   \item{
     \textbf{Backend \& APIs}{: RESTful API Design, OAuth2.0, FHIR/HL7, ActiveMQ, Microservices Architecture, SOLID Principles}
   }
   \item{
     \textbf{Databases \& Cloud}{: SQL Server, SQLite, PostgreSQL, AWS (Lambda, RDS, S3), Git, CI/CD}
   }
 \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------------
\section{Certifications}
 \resumeSubHeadingListStart
   \item{AWS Certified AI Practitioner}
   \item{AWS Certified Cloud Practitioner}
   \item{Unity Certified User: Game Programmer}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
