\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedright
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Alihan Baysal} & baysal.alihan@outlook.com \\
  \href{https://alihanbaysal.com}{alihanbaysal.com} & +1-541-740-9292 \\
\end{tabular*}

\vspace{10pt}

Dear Naughty Dog Hiring Team,

I'm writing to apply for the Web Tools Programmer position. I want to be upfront about something --- this isn't just another application for me. Naughty Dog is the reason I got into this field.

I grew up in Turkey, and when I first played Uncharted with the Turkish dub, it genuinely changed something in me. Hearing Nathan Drake speak my language, seeing a world-class game acknowledge that Turkish players existed --- that was priceless. It sounds small, but for a kid who spent most of his time around English-only media, it meant everything. That experience is what made me want to build things that reach people across the world.

I've been a full-stack engineer for the past few years, and the work I've done maps closely to what you're looking for. At my current role, I build and maintain internal web applications on AWS, manage database migrations at scale, and debug distributed system issues across services --- the same kind of infrastructure work that keeps a studio's tooling running. Before that, I spent over two years at Oregon State breaking apart a monolith into microservices, building front-end tools with Vue.js and TypeScript for internal teams, and writing the documentation that kept everything maintainable.

On the side, I've been building games in C++ with SDL3 and working through graphics programming with OpenGL. I'm also a Unity Certified Game Programmer, which I got because I wanted to understand game development from the engine level up. I'm not pretending to be a senior engine programmer, but I genuinely enjoy the low-level work and I'm actively growing in that direction.

What draws me to this role specifically is the total project ownership aspect --- from integrating with the game runtime, to architecting the backend, to shipping functional UIs for the dev team. That's exactly how I like to work. I care about making other developers' lives easier, and I'd love to do that for the people building the games I grew up on.

Thank you for your time. I'd love the chance to talk more about how I can contribute.

Best, \\
Alihan Baysal

\end{document}
